Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations

### 2017-08-18 Ben_Manuscripts/Masters_Bypass/results.tex
polishing

To discern the composition of the monomer layers, we ran simulations of 
systems created with 4 - 8 monomers per layer. Both the sandwiched and 
parallel displaced configurations were tested. All systems remained
stable for at least 50 ns. Pore spacings were calculated by measuring
the distance between the pore centers. Pore centers were located by
averaging the coordinates of sodium ions in their respective pores. 
Statistics were generated using the bootstrapping technique. Table
~\ref{table:p2p} shows the pore spacing for all systems tested.
Systems built with 5 monomers in each layer equilibrate to a pore
spacing that is most consistent with the experimental value of 4.12 nm
derived from SAXS measurements (Figure~\ref{fig:SAXS}). The remainder of
this discussion will focus on the analysis of systems built with 5 
monomers per layer. Pair correlation functions calculated between 
aromatic rings along the length of the pores indicate that systems
prefer to stay partitioned into layers (Fig~\ref{fig:zdf}).

\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
                   & \multicolumn{2}{c}{Starting Configuration} \\
\hline
Monomers per layer & Sandwiched & Parallel Displaced \\
\midrule
4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
5 & $3.99 \pm 0.04$ & $4.16 \pm 0.04$ \\
6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
\bottomrule
\end{tabular}
\caption{The pore spacing of the model increases as number of monomers
in each layer increases. The pore spacing of a system starting in the 
sandwiched configuration is systematically lower than that started in an 
offset configuration. Systems built with 5 monomers per layer in a parallel
displaced configuration results in a pore spacing closest to experimental
data}\label{table:p2p} 
\end{table}

@@

Basin A and Basin B are two configurationally metastable basins. 
We hesitate to classify the basins as separate phases. We hypothesize
that Basin B is present at higher temperatures. This is evidenced by
a simulation of a system in Basin A whose temperature was linearly
ramped from 280K to 340K over 100 ns. Visually, there is a distinct
change in pore structure from one characteristic of Basin A 
(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
three easily measurable order parameters: the distance between pores,
the membrane the thickness and the ratio of pore radius to the uncertainty
in pore radius. The distance between pores was measured as described 
previously. The membrane thickness was measured using the length of the
z box vector. The pore radius was measured by calculating the distance
between the center of mass of each aromatic ring and the center of mass
of all aromatic rings in their respective pores. The pore radius is divided by
its uncertainty in order to understand the degree to which monomers 
obstruct the pore region. Referring back to our temperature ramped system,
the slope of all order parameters change around 315K - 325K 
(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
possibility of an abrupt change in system ordering. To prove that the 
basins are in fact two different phases, we must observe evidence of a
first order phase transition, which would be marked by a discontinuity
in an order parameter as a function of temperature. Our 100 ns temperature
ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
hysteresis, we performed a slow, stepwise temperature ramp. Starting from
structures equilibrated at 280K, the system temperature was raised to 
300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
temperature was raised 5K and equilibrated again for 200 ns. We repeated
this process until the system was equilibrated for 200 ns at 320K. In all
cases, we observed smooth changes in order parameters as temperature was
increased implying that we can not yet claim the existence of two phases (Figure~\ref{fig:phase_transition}).
The same process will continue to be repeated up to 340K in the near future
since we have not surpassed the temperatures where we observe abrupt slope 
changes in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).

@@

>>>>

To discern the composition of the monomer layers, we ran simulations of 
systems created with 4 - 8 monomers per layer. Both the sandwiched and 
parallel displaced configurations were tested. All systems remained
stable for at least 50 ns. Pore spacings were calculated by measuring
the distance between the pore centers. Pore centers were located by
averaging the coordinates of sodium ions in their respective pores. 
Statistics were generated using the bootstrapping technique. Table
~\ref{table:p2p} shows the pore spacing for all systems tested.
Systems built with 5 monomers in each layer equilibrate to a pore
spacing that is most consistent with the experimental value of 4.12 nm
derived from SAXS measurements (Figure~\ref{fig:SAXS}). We verified 
that the system stays partitioned into layers by plotting pair 
correlation functions calculated between aromatic rings along the
length of the pores (Fig~\ref{fig:zdf}).The remainder of this 
discussion will focus on the analysis of systems built with 5
monomers per layer.

\begin{table}[H]
\centering
\begin{tabular}{ccc}
\toprule
                   & \multicolumn{2}{c}{Starting Configuration} \\
\hline
Monomers per layer & Sandwiched & Parallel Displaced \\
\midrule
4 & $3.71 \pm 0.04$ & $3.82 \pm 0.03$ \\
5 & $4.20 \pm 0.04$ & $4.23 \pm 0.04$ \\
6 & $4.83 \pm 0.03$ & $4.85 \pm 0.02$ \\
7 & $4.73 \pm 0.03$ & $4.84 \pm 0.03$ \\
8 & $5.08 \pm 0.04$ & $5.46 \pm 0.03$ \\
\bottomrule
\end{tabular}
\caption{The pore spacing of the model increases as number of monomers
in each layer increases. The pore spacing of a system starting in the 
sandwiched configuration is systematically lower than that started in an 
offset configuration. Systems built with 5 monomers per layer in a parallel
displaced configuration result in a pore spacing closest to experimental
data}\label{table:p2p} 
\end{table}

@@

@@

Basin A and Basin B are two configurationally metastable basins. 
We hesitate to classify the basins as separate phases. We hypothesize
that Basin B is present at higher temperatures. This is evidenced by
a simulation of a system in Basin A whose temperature was linearly
ramped from 280K to 340K over 100 ns. Visually, there is a distinct
change in pore structure from one characteristic of Basin A 
(Figure~\ref{fig:280K_pore}) to one characteristic of Basin B 
(Figure~\ref{fig:340K_pore}). To quantify our observation, we chose 
three easily measurable order parameters: the distance between pores,
the membrane the thickness and the ratio of pore radius to the uncertainty
in pore radius. The distance between pores was measured as described 
previously. The membrane thickness was measured using the length of the
z box vector. The pore radius was measured by calculating the distance
between the center of mass of each aromatic ring and the center of mass
of all aromatic rings in their respective pores. The pore radius is divided by
its uncertainty in order to understand the degree to which monomers 
obstruct the pore region. Referring back to our temperature ramped system,
the slope of all order parameters change around 315K - 325K 
(\Cref{fig:p2p_tramp,fig:thickness_tramp,fig:order_tramp}) indicating the 
possibility of an abrupt change in system ordering. To prove that the 
basins are in fact two different phases, we must observe evidence of a
first order phase transition, which would be marked by a discontinuity
in an order parameter as a function of temperature. Our 100 ns temperature
ramp may have been too fast causing the system to suffer from hysteresis. To mitigate
hysteresis, we performed a slow, stepwise temperature ramp. Starting from
a sandwiched structure equilibrated at 280K, the system temperature was raised to 
300K and allowed to equilibrate for 200 ns. At the end of 200 ns, the
temperature was raised 5K and equilibrated again for 200 ns. We continued raising the 
temperature by 5K and equilibrating for 200 ns until the system was 
equilibrated for 200 ns at 320K. In all cases, we observed smooth changes
in order parameters as temperature was increased implying that we can not yet
claim the existence of two phases (Figure~\ref{fig:phase_transition}). The same
process will continue to be repeated up to 340K in the near future since we have
not surpassed the temperatures where we have observed the abrupt slope changes
in pore spacing and membrane thickness (\Cref{fig:p2p_tramp,fig:thickness_tramp}).
